This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-05-02 article.tex
More text

\end{tikzpicture}}
\end{center}
The second through fourth most significant bits of the first byte are
used to store the object type. The remainder of the bytes in the
header are of the same format as bytes two and three in this
example. This example header represents an object of type $11_2$,
which happens to be a git blob, and an \emph{uncompressed} length of
$(100_2\,\verb|<<|\,14) + (1010110_2\,\verb|<<|\,7) + 1001001_2 =
76617$ bytes.  Since this is not a delta object, it is immediately
followed by the zlib-compressed object data. The header does not
encode the \emph{compressed} size of the object, since the DEFLATE
encoding can determine the end of the object as it is being
decompressed.

@@

Getting the object to be compressed with zero compression is also
relatively easy.  That's because git was built in almost religious
adherence to The UNIX Philosophy: It is architected with hundreds of
sub commands it calls ``plumbing,'' of which the vast majority you
will likely have never heard. For example, you might be aware
that \texttt{git pull} is equivalent to a \texttt{git fetch} followed
by a \texttt{git merge}. In fact, the \texttt{pull} code is actually
spawning a new \texttt{git} child process to execute each of those
subcommands. Likewise, the \texttt{git bundle} command spawns
a \texttt{git pack-objects} to generate the packfile portion of the
bundle.  All we need to do is inject the \texttt{--compression=0}
argument into the list of command line arguments passed
to \texttt{pack-objects}.  This is a one-line addition
to \texttt{bundle.c}:\\
{\footnotesize
{\color{gray}
\verb|    argv_array_pushl(&pack_objects.args,|\\
\verb|                     "pack-objects", "--all-progress-implied",|}\\
\verb|                     "--compression=0",|\\
{\color{gray}
\verb|                     "--stdout", "--thin", "--delta-base-offset",|\\
\verb|                     NULL);|
}}

@@

There are, of course, some

>>>>

\end{tikzpicture}}
\end{center}
The second through fourth most significant bits of the first byte are
used to store the object type. The remainder of the bytes in the
header are of the same format as bytes two and three in this
example. This example header represents an object of type $11_2$,
which happens to be a git blob, and an \emph{uncompressed} length of
$(100_2\,\verb|<<|\,14) + (1010110_2\,\verb|<<|\,7) + 1001001_2 =
76$,617 bytes.  Since this is not a delta object, it is immediately
followed by the zlib-compressed object data. The header does not
encode the \emph{compressed} size of the object, since the DEFLATE
encoding can determine the end of the object as it is being
decompressed.

@@

Getting the object to be compressed with zero compression is also
relatively easy.  That's because git was built in almost religious
adherence to The UNIX Philosophy: It is architected with hundreds of
sub commands it calls ``plumbing,'' of which the vast majority you
will likely have never heard. For example, you might be aware
that \texttt{git pull} is equivalent to a \texttt{git fetch} followed
by a \texttt{git merge}. In fact, the \texttt{pull} code actually
spawns a new \texttt{git} child process to execute each of those
subcommands. Likewise, the \texttt{git bundle} command spawns
a \texttt{git pack-objects} child process to generate the packfile
portion of the bundle.  All we need to do is inject
the \texttt{--compression=0} argument into the list of command line
arguments passed to \texttt{pack-objects}.  This is a one-line
addition to \texttt{bundle.c}:\\ {\footnotesize {\color{gray}
\verb|    argv_array_pushl(&pack_objects.args,|\\
\verb|                     "pack-objects", "--all-progress-implied",|}\\
\verb|                     "--compression=0",|\\
{\color{gray}
\verb|                     "--stdout", "--thin", "--delta-base-offset",|\\
\verb|                     NULL);|
}}

@@

There are, of course, several limitations to the minimal PoC given in
the previous section:
\begin{enumerate}

\item Adobe, being Adobe, will refuse to open the polyglot unless the PDF is version 1.4 or earlier.  I guess it doesn't like some element of the git bundle signature or digest if it's PDF~1.5? Why? Because Adobe, that's why.

\item Leaving the entire Git bundle uncompressed is wasteful if the repo contains other files; really, we only need the PDF to be uncompressed.

\item If the PDF is larger than 65,535 bytes---the maximum size of an uncompressed DEFLATE block---then git will inject 5-byte deflate block headers inside the PDF, likely corrupting it.

\item Adobe will also refuse to open the polyglot unless the PDF is near the beginning of the packfile\footnote{Requiring the PDF header to start near the beginning of a file is common for many, but not all, PDF viewers.}.

\end{enumerate}

The first limitation is easy to fix by instructing \LaTeX\ to produce
a version 1.4~PDF by adding \texttt{\textbackslash pdfminorversion=4}
to the document.

The second limitation is a simple matter of software engineering,
adding a command line argument to the \texttt{git bundle} command that
accepts the hash of the single file to leave uncompressed, and passing
that hash to \texttt{git pack-objects}. I have created a fork of git
with this feature, available here:
\begin{center}
  \texttt{https://github.com/ESultanik/git/tree/UncompressedPack}
\end{center}

As an aside, while fixing the second limitation I discovered that if a
file has multiple PDFs concatenated after one another
(\textit{i.e.},~a git bundle polyglot with multiple uncompressed PDFs
in the repo), then the behavior is viewer-dependent: Some viewers will
render the first PDF, while others will render the last.  That's a fun
way to generate a PDF that displays completely different content in,
say, macOS~Preview versus Adobe.

The third limitation is very tricky, and ultimately why this polyglot
was not used for the PDF of a digital issue of PoC$\|$GTFO. I've a
solution, but it will not work if the PDF contains any objects
(\textit{e.g.}, images) that are larger than 65,535 bytes. A universal
solution would be to break up the image into smaller ones and tile it
back together, but that is not feasible for a document the size of a
PoC$\|$GTFO issue.

DEFLATE headers for uncompressed blocks are very simple: The first
byte encodes whether the following block is the last in the file, the
next two bytes encode the block length, and the last two bytes are the
ones' complement of the length.  Therefore, to resolve this issue, all
we need to do is move all of the DEFLATE headers that zlib created to
different positions that won't corrupt the PDF, and update their
lengths accordingly.
